### 2021-10-27 SujetStage/2021-pNetsubjectM2.tex
explications de "holes and parameters"

In the previous years, we have studied theoretical foundations for open
systems and we defined  open automata \cite{arxiv-weakbisim,henrio:Forte2016,hou:hal-02406098} that can be seen as labelled transition systems (LTSs) with parameters and holes. The transitions of open
automata are much more complex than transitions of an LTS as the firing on a transition depends on parameters and actions that are symbolic.

>>>>

In the previous years, we have studied theoretical foundations for open
systems and we defined  open automata \cite{arxiv-weakbisim,henrio:Forte2016,hou:hal-02406098} that can be seen as labelled transition systems (LTSs) with parameters and holes. The transitions of open
automata are much more complex than transitions of an LTS: they include guards expressing the relations between the parameters of the automaton with the actions of the holes, and assignments encoding their effects.
% as the firing on a transition depends on parameters and actions that are symbolic.
Holes here are modeling the environment of the open automaton, that can be used to compose open automata together to build bigger systems. We proved that our models 
have good properties, namely that composition preserves some classes of equivalences.
